---
title: "hw2"
author: "mh3658"
date: "March 21, 2017"
output: html_document
---

First, read in the 1-min S&P500 E-Mini and FTSE-100 index futures data. 

```{r}
setwd("D:\\Columbia 17spring\\math mthd in fin\\Lecture _4")
ES<-read.csv("ES.asc", header = TRUE)
FT<-read.csv("FT.asc", header = TRUE)

espx = ES$Close
ftpx = FT$Close

```


For tau=1, do the hist and log-plot. First, normalized the result, then graph the result on a log-lin scale, also superimpose the true gaussian pdf (in red line). It can be clearly tell by the graph that the non-gaussian fat-tails exists in the PDF

Also, create vector es\_p and ft\_p to store the log-probability value when x=0. These data would be useful when we estimate alpha in the next problem.

```{r}
espxdiff = diff(espx, lag=1)
hist(espxdiff)
ftpxdiff = diff(ftpx, lag=1)
hist(ftpxdiff)

eslen = length(espxdiff)
ftlen = length(ftpxdiff)

esdist <- table(espxdiff)/eslen
ftdist <- table(ftpxdiff)/ftlen

esdist<-as.data.frame(esdist)
ftdist<-as.data.frame(ftdist)

sigma1 = sqrt(var(espxdiff))
sigma2 = sqrt(var(ftpxdiff))
mu1 = mean(espxdiff)
mu2 = mean(ftpxdiff)

taus = c(1,5,30,60,120,180,360)

library(ggplot2)
x_es=as.numeric(as.character(esdist$espxdiff))
y_es=log10(esdist$Freq)
norm_es = log10(dnorm(x_es,mu1,sigma1))

es_p<-c(y_es[x_es==0])

q<-ggplot()+geom_point(data= data.frame(x_es, y_es),aes(x_es,y_es))+geom_line(data = data.frame(x_es,norm_es),aes(x_es,norm_es),colour="red")+xlim(c(-50,50))+ylim(c(-7,0))
q

x_ft=as.numeric(as.character(ftdist$ftpxdiff))
y_ft=log10(ftdist$Freq)
norm_ft = log10(dnorm(x_ft,mu2,sigma2))

ft_p<-c(y_ft[x_ft==0])

q1<-ggplot()+geom_point(data= data.frame(x_ft, y_ft),aes(x_ft,y_ft))+geom_line(data = data.frame(x_ft,norm_ft),aes(x_ft,norm_ft),colour="red")+xlim(c(-150,150))+ylim(c(-7,0))
q1

```

to further develop graph for tau = 5, 30, 60, 120, 180, 360, first re-writing the graph process into a function. Also, keep the probability value for x=0 while doing the graph.

```{r}
graph <- function(tau = 1, dataset){
  dif = diff(dataset, lag=tau)
  dist<-as.data.frame(table(dif)/length(dif))
  sd = sqrt(var(dif))
  mu = mean(dif)
  
#  library(ggplot2)
  x=as.numeric(as.character(dist$dif))
  y=log10(dist$Freq)
  norm = log10(dnorm(x,mu,sd))
  
  # t here is the probability when x=0. This is for calculating the alpha
  t<-y[x==0]
  q<-ggplot()+geom_point(data= data.frame(x, y),aes(x,y))+geom_line(data = data.frame(x,norm),aes(x,norm),colour="red")+xlim(c(-150,150))+ylim(c(-7,0))
  
  t
  q
}

```

redo the problem for different taus

```{r}
graph(5, espx)
graph(30, espx)
graph(60, espx)
graph(120, espx)
graph(180, espx)
graph(360, espx)

graph(5, ftpx)
graph(30,ftpx)
graph(60,ftpx)
graph(120,ftpx)
graph(180,ftpx)
graph(360,ftpx)

```

Using the leading-order term from the formula for the taylor-series expansion of the Levy PDF. Infer the Levy exponent alpha for both of the ES and FT markets.

for different tau value, we can get their probability at x=0, which shows above. Collect them into es_p and ft_p (R seems to not have a passing by reference for function, so I have to do it in this dumb way)

To estimate alpha, we try to do regression for log10(P(x=0)) to log10(tau). According to the leading term of our Levy distribution PDF, the slope for this regression is -1/alpha. 


```{r}
es_p <- c(es_p, -0.9423310, -1.3335781,-1.482897,-1.6550708,-1.7809320,-1.9871224)
ft_p<-c(ft_p, -1.130673, -1.524275,-1.68808, -1.856656, -1.971874, -2.221174)

plot(es_p, log10(taus),type='o')
plot(ft_p, log10(taus),type='o')

esreg <- lm(es_p~log10(taus))
ftreg<-lm(ft_p~log10(taus))

es_alpha = as.numeric(-1/(esreg$coefficients[2]))
es_alpha
ft_alpha = as.numeric(-1/(ftreg$coefficients[2]))
ft_alpha
```

so we can see that es_alpha equals 1.917878
ft_alpha equals 1.824196